Data Analysis and Modelling of Teen Vaccination Surveys

### 2024-05-03 code/analysis-code/analysis2.qmd
Updated figures

# Combine the training and test metrics data frames
combined_metrics_df <- rbind(train_metrics_df, test_metrics_df)

# Create a gt table
gt_table <- combined_metrics_df %>%
  gt(
    groupname_col = "Dataset", 
    row_group_as_column = TRUE
  ) %>%
  tab_header(
    title = md("Model Evaluation Metrics"),
    subtitle = md("Comparison of Metrics between Test and Training Datasets")
  )

>>>>

# Combine the training and test metrics data frames
combined_metrics_df <- rbind(train_metrics_df, test_metrics_df) %>%
  filter(Metric %in% c("MSE", "R^2", "AUC"))

# Create a gt table
gt_table <- combined_metrics_df %>%
  gt(
    groupname_col = "Dataset", 
    row_group_as_column = TRUE
  ) %>%
  tab_header(
    title = md("Model Evaluation Metrics"),
    subtitle = md("Comparison of Metrics between Test and Training Datasets")
  )%>%
  fmt_number(
    decimals = 3  
  )
